\textbf{Generalized additive models to analyze biomedical non-linear longitudinal data in R: Beyond repeated measures ANOVA and Linear Mixed Models}

### 2021-12-10 Code and miscellaneous/Simultaneous-interval-differences.Rmd
Uncommented the "zero parametric cols" line in Section: Longitudinal data analysis with GAMs

    xp <- predict(gam_02, newdata = newdata, type = 'lpmatrix')
    #Find columns in xp where the name contains "Control" and "Treatment"
    col1 <- grepl("Control", colnames(Cg))
    col2 <- grepl("Treatment", colnames(Cg))
    #Find rows in xp that correspond to each treatment
    row1 <- with(newd, Group == "Control")
    row2 <- with(newd, Group == "Treatment")
    ## difference rows of xp for data from comparison
    X <- Cg[row1, ] - Cg[row2, ]
    ## zero out cols of X not involved in the comparison
    X[, ! (col1 | col2)] <- 0
    ## zero out the parametric cols
    #X[, !grepl('^s\\(', colnames(Cg))] <- 0
    dif <- X %*% coef(gam_02)
    se <- sqrt(rowSums((X %*% vcov(gam_02, unconditional = TRUE)) * X))
    crit <- qt(0.05/2, df.residual(gam_02), lower.tail = FALSE)
    upr <- dif + (crit * se)
    lwr <- dif - (crit * se)
   comp1<- data.frame(pair = paste("Control", "Treatment", sep = '-'),
               diff = dif,
               se = se,
               upper = upr,
               lower = lwr)

>>>>

    xp <- predict(gam_02, newdata = newdata, type = 'lpmatrix')
    #Find columns in xp where the name contains "Control" and "Treatment"
    col1 <- grepl("Control", colnames(Cg))
    col2 <- grepl("Treatment", colnames(Cg))
    #Find rows in xp that correspond to each treatment
    row1 <- with(newd, Group == "Control")
    row2 <- with(newd, Group == "Treatment")
    ## difference rows of xp for data from comparison
    X <- Cg[row1, ] - Cg[row2, ]
    ## zero out cols of X not involved in the comparison
    X[, ! (col1 | col2)] <- 0
    ## zero out the parametric cols
    X[, !grepl('^s\\(', colnames(Cg))] <- 0
    dif <- X %*% coef(gam_02)
    se <- sqrt(rowSums((X %*% vcov(gam_02, unconditional = TRUE)) * X))
    crit <- qt(0.05/2, df.residual(gam_02), lower.tail = FALSE)
    upr <- dif + (crit * se)
    lwr <- dif - (crit * se)
   comp1<- data.frame(pair = paste("Control", "Treatment", sep = '-'),
               diff = dif,
               se = se,
               upper = upr,
               lower = lwr)

### 2021-12-10 Manuscripts/Manuscript_by_chapters-SIM_Revisions/sections/04-Longitudinal analysis with GAMs.Rmd
Uncommented the "zero parametric cols" line in Section: Longitudinal data analysis with GAMs

smooth_diff <- function(model, newdata, g1, g2, alpha = 0.05,
                        unconditional = FALSE) {
    xp <- predict(model, newdata = newdata, type = 'lpmatrix')
    #Find columns in xp where the name contains "Control" and "Treatment"
    col1 <- grepl(g1, colnames(xp))
    col2 <- grepl(g2, colnames(xp))
    #Find rows in xp that correspond to each treatment
    row1 <- with(newdata, Group == g1)
    row2 <- with(newdata, Group == g2)
    ## difference rows of xp for data from comparison
    X <- xp[row1, ] - xp[row2, ]
   ## zero out cols of X not involved in the comparison
    X[, ! (col1 | col2)] <- 0
    ## zero out the parametric cols
    #X[, !grepl('^s\\(', colnames(xp))] <- 0
    dif <- X %*% coef(model)
    se <- sqrt(rowSums((X %*% vcov(model, unconditional = unconditional)) * X))
    crit <- qt(alpha/2, df.residual(model), lower.tail = FALSE)
    upr <- dif + (crit * se)
    lwr <- dif - (crit * se)
    data.frame(pair = paste(g1, g2, sep = '-'),
               diff = dif,
               se = se,
               upper = upr,
               lower = lwr)
}

>>>>

smooth_diff <- function(model, newdata, g1, g2, alpha = 0.05,
                        unconditional = FALSE) {
    xp <- predict(model, newdata = newdata, type = 'lpmatrix')
    #Find columns in xp where the name contains "Control" and "Treatment"
    col1 <- grepl(g1, colnames(xp))
    col2 <- grepl(g2, colnames(xp))
    #Find rows in xp that correspond to each treatment
    row1 <- with(newdata, Group == g1)
    row2 <- with(newdata, Group == g2)
    ## difference rows of xp for data from comparison
    X <- xp[row1, ] - xp[row2, ]
   ## zero out cols of X not involved in the comparison
    X[, ! (col1 | col2)] <- 0
    ## zero out the parametric cols
    X[, !grepl('^s\\(', colnames(xp))] <- 0
    dif <- X %*% coef(model)
    se <- sqrt(rowSums((X %*% vcov(model, unconditional = unconditional)) * X))
    crit <- qt(alpha/2, df.residual(model), lower.tail = FALSE)
    upr <- dif + (crit * se)
    lwr <- dif - (crit * se)
    data.frame(pair = paste(g1, g2, sep = '-'),
               diff = dif,
               se = se,
               upper = upr,
               lower = lwr)
}
